\chapter{Application requirements}
\label{sec:application_requirements}
The application requires a few things in order to run.

\section{Server side}
\begin{description}
\item[Web server] A web server is needed in order to run the web site. It is also required to have permissions to run executables. The included data parser is compiled for Windows, OSX and Ubuntu. If the web server is not allowed to run the included executables, they should be ran as a CGI script - This has not been tested however.
\item[PHP] The web server should support PHP version 5.3+.
\item[GD] The application uses GD\footnote{GD Image library. See \cite{GD} for a more in depth explanation} 2.0.1+ (2.0.28+ is recommended) to create radar images.
\item[MySQL] FuelPHP\footnote{See \cite{FuelPHP} for more documentation} supports multiple databases through drivers, but in order to support time zones correctly, we've chosen to take advantage of MySQLs own methods. This means that MySQL 5.5.20+ is required.
\item[Zoneinfo] MySQL\footnote{A relational database management system. See \cite{MySQL}} needs Zoneinfo\footnote{Zoneinto is information about timesonzes used by the application to convert between timezones. See \cite{Zoneinfo} for explanation} in order for the time zones to work properly\footnote{On linux, the following command can be executed in the terminal to import zoneinfo: \mbox{\textsf{> mysql\_tzinfo\_to\_sql /usr/share/zoneinfo | mysql -u root -p mysql}}. Other operating systems might not have the zoneinfo, and will have to download it from \cite{Zoneinfo_download} and import it to the mysql database. See \cite{Zoneinfo_install} for installation notes}
\item[Safe mode] Safe mode might need to be disabled in the PHP configuration, if \textsf{fopen}\footnote{See \url{http://php.net/manual/en/function.fopen.php}.} is not allowed to access some files.
\end{description}

\section{Client side}
\begin{description}
\item[JavaScript] It is required that the users browser supports and has enabled JavaScript in order for the site to work.
\end{description}