\chapter{Requirements}
We stated some requirements to the final product, that should be fulfilled. 
The requirements:
\begin{itemize}
\item Web based software using opensource software.
\item Upload data to server in seperate files and compressed files.
\item Analyse and read data from CSV, WRK and NC-files.
\item Visualize the data in a nice user-friendly way.
\item Several performance requirements
\end{itemize}
We created the web based software using opensource.\\
It is allowed to upload CSV, WRK and zip-files.\\
We didn't do the implementation for the NC-files, because of difficulty and time pressure. However, CSV and WRK-files are working just fine, even if they both are compressed into one zip-file.\\
The visualizing of data are done in very user-friendly and cool design. We used a lot javascript, to create this cool and user-friendly design.\\
The performance is very good and the server is doing the most work, so even computers with poor specifications can access. We have done some caching\footnote{A collection of data duplicating original values stored on the server or by the client's web browser}, to get better performance too.\\

\section{Application requirements}
\label{sec:application_requirements}
The application requires a few things in order to run.
\begin{description}
\item[Web server] A web server is needed in order to run the web site. It is also required to have permissions to run executables. The included data parser is compiled for Windows, OSX and Ubuntu. If the web server is not allowed to run the included executables, they should be ran as a CGI script - This has not been tested however.
\item[PHP] The web server should support PHP version 5.3+.
\item[GD] The application uses GD 2.0.1+ (2.0.28+ is recommended) to create radar images.
\item[MySQL] FuelPHP supports multiple databases through drivers, but in order to support time zones correctly, we've chosen to take advantage of MySQLs own methods. This means that MySQL 5.5.20+ is required.
\item[Zoneinfo] MySQL needs Zoneinfo in order for the time zones to work properly\footnote{On linux, the following command can be executed in the terminal to import zoneinfo: \mbox{\textsf{> mysql\_tzinfo\_to\_sql /usr/share/zoneinfo | mysql -u root -p mysql}}. Other operating systems might not have the zoneinfo, and will have to download it from \url{http://dev.mysql.com/downloads/timezones.html} and import it to the mysql database.}
\item[Safe mode] Safe mode might need to be disabled in the PHP configuration, if \textsc{fopen}\footnote{See \url{http://php.net/manual/en/function.fopen.php}.} is not allowed to access some files.
\end{description}