\chapter{Use case}
We have two types of actor:
\begin{itemize}
\item User: Person like everyone else. A user who doesn't have special permissions.
\item Admin: Person with permission to files upload and user management.
\end{itemize}

\subsection{Clicking on a radar}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{itemize}
\item Checks if there is data for the date
\item If images isn't generated, it will generate them real time.
\item Radar shows images over an interval.
\item \emph{One click for play/pause and doubleclick for reset.}
\item When there is no more data, the radar resets.
\end{itemize}
\textbf{Alternative scenario:} 
\begin{enumerate}
\item No data is available for that moment and a message appears.
\end{enumerate}

\subsection{Clicking on a wind farm}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{itemize}
\item Visualize data for that given wind farm.
\end{itemize}

\subsection{Changing view in chart}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{enumerate}
\item Changing to 2-week view.
\begin{itemize}
\item Changing chart view interval to 2 weeks.
\item Load new data for the new interval.
\end{itemize}
\item Changing to weekly view.
\begin{itemize}
\item Changing chart view interval to 1 week.
\item Load new data for the new interval.
\end{itemize}
\item Changing to daily view.
\begin{itemize}
\item Changing chart view interval to 1 day.
\item Load new data for the new interval.
\end{itemize}
\end{enumerate}

\subsection{Show/hide data in chart}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{itemize}
\item Data is shown.
\end{itemize}
\textbf{Alternative scenario}
\begin{enumerate}
\item Data is removed.
\end{enumerate}

\subsection{Using control buttons in chart}
\textbf{Actor:} User

\textbf{Scenario:}
\begin{enumerate}
\item Pressing fast backward.
\begin{itemize}
\item Go two weeks back on 2-week view, one week back on weekly view and one day on daily view.
\item Loads new data.
\end{itemize}
\item Pressing backward.
\begin{itemize}
\item Go one week back on 2-week view, one day back on weekly view and one hour on daily view.
\item Loads new data.
\end{itemize}
\item Pressing play.
\begin{itemize}
\item Change to daily view and go one hour forward every second.
\item Loads new data.
\end{itemize}
\item Pressing forward.
\begin{itemize}
\item Go one week forward on 2-week view, one day forward on weekly view and one hour on daily view.
\item Loads new data.
\end{itemize}
\item Pressing fast forward.
\begin{itemize}
\item Go two weeks forward on 2-week view, one week forward on weekly view and one day on daily view.
\item Loads new data.
\end{itemize}
\end{enumerate}

\subsection{Upload file}
\textbf{Actor:} Admin

\textbf{Scenario:}
\begin{itemize}
\item Sign in with correct username and password.
\item Add new file (CSV, WRK, ZIP) and enter correct timezone.
\item If file is ZIP, it will decompress.
\item File is uploaded.
\item File is being parsed.
\end{itemize}
\textbf{Alternative scenario:} 
\begin{enumerate}
\item Sign in with wrong username or password.
\item Adding file that isn't correct format and get an error message.
\item Adding ZIP file, but files inside zip isn't correct. It will get an error message.
\item File exists and will not be uploaded.
\end{enumerate}