\chapter{Work flow \& distribution}
\label{work_flow_and_distribution}
At the beginning Dropbox\footnote{A web based file hosting service - see \cite{Dropbox}} was used for sharing files between group members, using a shared folder, all members could read and write to. It was fine at the beginning, but later when there became file conflicts , it started to get a little problematic, since Dropbox doesn't have a smart merging algorithm.
There was created a public repository at Git\footnote{A web based hosting service - see \cite{Git}} to push and pull data to the git server, so files could be changed without to many conflicts. Git was used, because of the merging algorithm and easy to use.

Git allows you to view older files and list commits\footnote{Every time a person push data to Git, he also gives a comment of what he has done. In that way it is easier to get an overview of changes.} from users through the whole project.

Git also allow other users to look at the program and and test it by themselves, so it is accessible for all.

Since Git is used, everyone can access the repository\footnote{Repository \url{http://github.com/connors511/WeatherDataVisualization}} by themselves. Users can't change or commit data, but can download the application and give comments to the project.

\section{Distribution}
\label{sec:distribution}
As this software project has been carried out by a group, we have been working together as a team with constructive criticism of each other, spelling and syntax correction ect. This means that everyone has more or less had a hand in every part of the software. However:

Mads Lundt has had the main responsibility of the following parts of the software:
\begin{itemize}
\item Map (HTML + JavaScript)
\item Report sections: \ref{ap:usecase}
\end{itemize}

Matthias Larsen has had the main responsibility of the following parts of the software:
\begin{itemize}
\item Data Parser (C++)
\item Report sections: \ref{sec:radar_interaction}, \ref{sec:the_cpp_application}, \ref{sec:radar_annotation}, \ref{sec:caching}, \ref{sec:cross-platform}, \ref{sec:file_type_support} through \ref{sec:data_date_range}, \ref{sec:api}, \ref{sec:restrictions_and_limitations}, \ref{sec:application_requirements}, \ref{ap:csv}
\end{itemize}

Joachim Jensen has had the main responsibility of the following parts of the software:
\begin{itemize}
\item File upload (PHP)
\item Report sections: \ref{ap:installation}
\end{itemize}